The Exoplanet Orbit Database \textsc{II}: updates for 2014

### 2014-03-25 draft/ms.tex
Revision 1

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}
\def\mjup{$M_{\rm Jup}$}
\def\rearth{R_\oplus}

@@

\title{The Exoplanet Orbit Database \textsc{II}: 2014 updates}

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ying Feng\altaffilmark{1,2}}
\author{Ming Zhao\altaffilmark{1,2}}
\author{Onsi Fakhouri}
\author{and Friends}

\altaffiltext{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA;
  Send correspondence to datamaster@exoplanets.org.}
\altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{3}{Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA}

@@

The Exoplanet Orbit Database (EOD) collects orbital and stellar
parameters of all known robustly dected exoplanets reported in the peer-reviewed
literature. The EOD can be navigated through the Exoplanet Data
Explorer (EDE) Plotter and Table, available at exoplanets.org. We have
ZZZ number of confirmed exoplanets as of March 2014.  
The first complete documentation for the EOD and the EDE was
\cite{Wright2011} and since then, we have expanded the scope of the
EOD. We also incorporated the sample of over 3000 \kepler\ Objects of
Interest (KOIs) and other planets (the ones detected by microlensing,
imaging, and timing) on exoplanets.org. We added some new fields
(e.g. the secondary eclipse depths), removed obsolete fields, and
revised some fields as necessary. The website also has gone through
some backend changes. The users can download the whole dataset as a
single .csv file from the front page of exoplanets.org.

@@

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of March 2014 (exoplanets.org). \kepler\ contributed to a vast
majority of these new discoveries ($> 800$) while providing an
additional sample of over 3000 exoplanet candidates (\kepler\ Objects
of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has
surpassed the radial velocity (RV) method and become the most fruitful
mean for detecting exoplanets. Meanwhile, great promises lie within
the new and future exoplanet surveys and instruments with direct
imaging (e.g., the Gemini Planet Imager, GPI,
\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
fronts of RV and transit exoplanet searches keep expanding (e.g., the
MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; and the
Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).

% The business of tracking planet discoveries and EOD
This paper describes the continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database (EOD)
and the Exoplanets Data Explorer (EDE) to keep track of the exoplanet
discoveries and to catalog their orbital parameters and host star
properties. There are also other entities devoted to this effort,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011} and the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
dedicated to cataloging all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature.

% data access and popularity
The EOD is hosted by exoplanets.org, which also hosts the EDE, an
interactive table with plotting tools including all the EOD exoplanets
as well as other confirmed exoplanets (and now also KOIs). The entire
dataset of exoplanets.org is available for download as a single {\tt
  .csv} file at the website's front page.\footnote{At
  \url{exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
used in exoplanet researches (e.g., \citealt{Dawson2013},
\citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
\citealt{Weiss2014}), and the website exoplanets.org is among the most
visited exoplanet databases, with over $47,000$ visitors in 2013
according to Google Analytics.

% updates on EOD and the website
Since \cite{Wright2011}, the EOD has expanded its scope: we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). It has also ingested more
parameters describing the exoplanet systems and their host stars, and some
parameters are revised or deleted. We describe the updates with the
EOD in Section~\ref{sec:update}. The EDE at exoplanets.org has also
expanded its scope and now includes the \kepler\ exoplanet candidates
(KOIs). We describe these changes in Section~\ref{sec:kepler}. The
website exoplanets.org has gone through major back-end changes since
\cite{Wright2011}, which is described in Section~\ref{sec:website}. We
summarize the updates and possible future improvements in
Section~\ref{sec:summary}.

@@

The scope of the EOD has expanded, and there are three major changes
from what was described in \cite{Wright2011}. Previously, we only
included exoplanets orbiting the ``normal stars", but now we are not
limiting the type of host stars (e.g. we included exoplanets orbiting
neutron stars). Furthermore, in \cite{Wright2011}, we only had
exoplanets that were discovered by the RV and transit methods in the
EOD, but now we also have planets discovered via timing. For the
future, exoplanets discovered by any other methods with robust
detections and good orbital parameters will also be included in the
EOD. Previously, we required the planets to be smaller than 24
\mjup, but now we require the mass ratio to be smaller than 24
\mjup$/\msun$ ($< 0.023)$.

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to have robust detections and well-determined
orbits (though these are not strictly quantitative; see Section~2 of
\citealt{Wright2011}). When new evidence comes to light and we are no
longer confident about the planet, we remove it from EOD, even if the
evidence is not peer reviewed.

The purpose of the EOD has not changed: we aim to provide the readers
with a comprehensive, reliable, and up-to-date database of exoplanets
with good orbital parameters and host star properties. We do not
report \textit{all} the announced exoplanets as we are not trying to
do ``an encyclopedic presentation of every claimed detection of an
exoplanet" \citep{Wright2011}.

In the following subsections, we describe the newly added and revised
fields since \cite{Wright2011}, but list all fields in
Table~\ref{tab:par}. We divide the fields into categories in
consistency with the individual planet page on
exoplanets.org. Figure~\ref{fig:individual} is an example of
individual planet page. Some fields are not explicitly tabulated on
the page (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file (see Section~\ref{sec:intro}). Though we
focus on the EOD in this section, the fields apply to all planets on
exoplanets.org. We follow the definition of orbital elements in
\cite{Wright2013} unless indicated otherwise.

@@

We report general information of when, by whom and how the planets
were discovered and provide the references. We describe the added or
revised fields since \cite{Wright2011} below.

{\bf DISCMETH} field previously reported the method of discovery,
which was either radial velocity or transit. We have replaced DISCMETH
with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better
report how exoplanet systems and individual exoplanets are first
discovered. PLANETDISCMETH reports the discovery method for the
planet, wihle STARDISCMETH reports the discovery method for the first
discovered planet around the host star. Furthermore, they are stored
in string formats and have values of one of the following: RV,
Transit, Imaging, Microlensing, Timing, or Astrometry.

{\bf MONTH} field reports the month in integer of when the
peer-reviewed paper is accepted by the journal.

{\bf KEPID} stands for KEPler ID, which is the integer number assigned
for a Kepler host star. KEPID is only available for the unconfirmed
KOI which we import directly from the Exoplanet Archive. Therefore,
none of the EOD planets and the confirmed Kepler planets has KEPID.

{\bf KOI} stands for Kepler Objects of Interest, which is an object
with transit signals detected by \kepler\ but have not been confirmed
to be due to exoplanets. The KOI field contains a floating point
number that consist of a whole number designated to the host star
followed by a decimal number denoting a candidate planet. For example,
KOI 102 is a star suspected to host two exoplanets, and KOI 102.01 is
the inner planet candidate and KOI 102.02 is the outer one. Once a
candidate is confirmed, the NAME field of the planet is replaced by
the official \kepler\ ID (``Kepler" followed by a hyphen, an integer
and an lower case letter). The KOI number is then used as
OTHERNAME. None of the KOIs are in the EOD. For more information, see
Section~\ref{sec:kepler}.

{\bf EOD} is a flag which indicates whether an exoplanet is included
in the EOD for having robust detection and well-characterized orbital
parameters such as the orbital period (PER). EOD equals 1 means the
exoplanet is in the EOD. We added this field because exoplanets.org
now also includes robustly discovered planets that do not have
well-characterized orbits, and also \kepler\ planet candidates (see
Section~\ref{sec:kepler} for more details).

{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
indicate that a planet detected via theses methods. For example,
MICROLENSING $=$ 1 means the planet is detected in a microlensing
event. However, we require the detection to be robust, as determined
by the QUAlity Control Board of the Exoplanet Database, QUACBED (see
Section~\ref{sec:kepler}).

%------------------------------------------------------------------------------
\subsection{Orbital Parameters}\label{sec:orbit}

We report the orbital parameters that determine the shape of the
planet's orbit. Depending on the detection methods, different sets of
parameters are given by the literatures. For instance, if a planet is
detected by the radial velocity method, the semiamplitude, $K$, is
reported whereas the inclination of the orbit, $i$, is reported by the
transit method. We describe the added fields since \cite{Wright2011}
below.

{\bf MASS} is the mass of the planet in the unit of Jupiter
mass. Previously, we only reported the minimum mass, ($m\sin{i}$,
MSINI) of the planets. We now report the mass as well when it is
available. For example, if a planet is discovered by microlensing, we
report the actual mass of the planet according to the literature. If a
planet has both radial velocity and transit measurements, we calculate
the mass from the minimum mass $m\sin{i}$ and the orbital inclination
$i$. MASS is set to MSINI if the orbital inclination is not given and
the reference for MASS, MASSREF is set to ``Set to MSINI; I unknown''.

For KOIs without MSINI measured, we calculate their mass using the
mass-radius relation from the literatures. For KOIs with $R<4\rearth$,
we follow \cite{Weiss2014}; for $4\rearth<R<6\rearth$, we follow
\cite{Lissauer2011}; and for $6\rearth<R<11.7\rearth$ we follow
\cite{Mordasini2012}.

{\bf SEP} is the projected separation on the sky between the host star
and the planet in the unit of AU. For directly imaged planets, the
literatures usually report the projected separation and we report the
value accordingly.  If SEP is not directly measured but the semi-major
axis ($a$, A) is available, then SEP is set to A with its reference,
SEPREF, set to ``Set to A''.

{\bf I} is the orbital inclination. Previously, only transiting
systems have I measured, but now some non-transiting systems
have I's reported too. For example, one microlensing system,
OGLE-2006-BLG-109L, has I measured \citep{Bennett2010}.

{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in the
unit of degree. At the moment, this is only measured for some of the
directly imaged planets, which are not in the EOD.

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the plane of the sky in the unit of degree. At the moment, $\lambda$
values are only available for the transiting systems, which are
measured by either the Rossiter-McLaughlin effect
\citep[e.g.,][]{Winn2005} or planet transiting star spots
\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is introduced because
the true spin-orbit angle ($\phi$), defined as the angle between the
stellar spin axis and the orbital axis, is normally not directly
measurable. We follow the definition of $\lambda$ in
\cite{Fabrycky2009} where the coordinates are defined as follows: the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field but we describe it here because it was not
reported consistently since some literatures report the ``projected
spin-orbit misalignment" as $\beta = -\lambda$ instead. We have sorted
these cases out and made sure that our $\lambda$'s are following the
definition of \cite{Fabrycky2009}.

@@

We report the transit parameters, which are available only when the
planet has TRANSIT flag equal to 1. We describe added fields since
\cite{Wright2011} below.

@@

{\bf RR} is the ratio of the planetary radius and the stellar
radius. If the transit depth (DEPTH) is not given, we calculate DEPTH
by taking square of RR but we do not calculate RR from DEPTH.

@@

We have added an entirely new set of fields for the secondary
eclipse. Previously, due to the limits of instrumentation and limited
sample of exoplanets, there were not much secondary eclipse depth data
available. Since \cite{Wright2011}, as many different surveys have
been launched, more and more secondary eclipse depths at multiple
bands become available for more and more planets. Therefore, we added
this entire new set of fields. ZZZ Refer to Ming's SE plot.

{\bf SE} flag indicates whether the system has detected secondary
eclipse in any of the two Micron All-Sky Survey (2MASS;
\citealt{Skrutskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
and 4 Spitzer IRAC bands. SE is a boolean and SE $=$ 1 indicates the
system has at least one detected secondary eclipse.

{\bf SEDEPTHX} whereas X stands for one of J H KS KP 36 45 58 80:
these fields are the secondary eclipse depth measured in the
corresponding wavelength band. SEDEPTHJ, H, and KS are the depths
measured in the 2MASS wavelength band in near infrared each centered
at 1.25~\micron, 1.65~\micron, and 2.15~\micron, respectively. KP is
the depth measured in the \kepler\ photometry band which ranges from
400 to 865~nm. The rest four stand for the Spitzer bands centered at
3.6~\micron, 4.5~\micron, 5.8~\micron, and 8.0~\micron.

{\bf SET} is the epoch of secondary eclipse center (normally in HJD).

@@

This set of parameters is to provide users the physical parameters of
the exoplanet host stars.  Most of the parameters are derived from the
stellar models in the literatures and we provide the readers with the
references. We describe added fields since \cite{Wright2011} below.

{\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of
the planetary system and is reported in km/s.

{\bf RSTAR} is the radius of the star in the solar radius.

{\bf RHOSTAR} is the density of the star in the unit of g/cm$^3$.

@@

We provide the brightness of the host star measured in different
wavelengths. We report optical magnitude and color ($V$ and $B-V$),
2MASS $J$, $H$, and $K_s$ magnitudes and we added {\bf KP} since
\cite{Wright2011}, which is the stellar magnitude measured through the
\kepler\ bandpass.

@@

We report the coordinates of the host star as well as the host star's
ID as designated by different catalogs.  We added {\bf DIST} since
\cite{Wright2011}, which is the distance to the host star in the unit
of pc. If only parallax (PAR) is given, we calculate DIST based on PAR
and vice versa. If the literature does not report DIST or PAR, then we
obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009}. We
naively propagate the error in PAR to DIST and vice versa.

@@

We have changed the way of reporting uncertainties, especially
asymmetric error bars since \cite{Wright2011}. We now report
uncertainties for a certain field X as XUPPER, XLOWER and UX. XUPPER
and XLOWER store the upper and lower 1$\sigma$ uncertainties, and they
are different when the error bars are asymmetric. UX contains the
1$\sigma$ uncertainty, and it equals to $({\rm XUPPER+XLOWER})/2$ in
the case of asymmetric error bars. Fields that have XUPPER, XLOWER and
UX are: all the orbital parameters except for TREND and FREEZE\_ECC
flags; all the transit parameters except for TRANSIT flags; all the
secondary eclipse fields except for SE flag; and all the stellar
properties except for STAR, SPECREF and BINARY flag; and DIST and PAR.

>>>>

% definition of symbols
\def\beq{\begin{equation}}
\def\eeq{\end{equation}}
\def\ergcms{erg~cm$^{-2}$~s$^{-1}$}
\def\ergs{erg~s$^{-1}$}
\def\mps{m~s$^{-1}$}
\def\msun{M_{\odot}}
\def\lsun{L_{\odot}}
\def\etal{~et~al.~}
\def\degree{^{\circ}}
\def\leq{\leqslant}
\def\geq{\geqslant}
\def\micron{$\mu$m}
\def\percm2{{\rm cm^{-2}}}
\def\peryr{yr$^{-1}$}
\def\kepler{\textit{Kepler}}
\def\spitzer{\textit{Spitzer}}
\def\micron{$\mu$m}
\def\mjup{$M_{\rm Jup}$}
\def\rearth{R_\oplus}
\def\mearth{M_\oplus}

@@

\title{The Exoplanet Orbit Database \textsc{II}: updates for 2014}

% leading authors
\author{Eunkyu Han\altaffilmark{1,2}}
\author{Sharon X. Wang\altaffilmark{1,2,3}}
\author{Jason T. Wright\altaffilmark{1,2,3}}
\author{Ying Feng\altaffilmark{1,2}}
\author{Ming Zhao\altaffilmark{1,2}}
\author{and Friends}

\altaffiltext{1}{Department of Astronomy \& Astrophysics, 525 Davey
  Lab, The Pennsylvania State University, University Park, PA 16802, USA;
  Send correspondence to jtwright@astro.psu.edu.}
\altaffiltext{2}{Center for Exoplanets and Habitable Worlds, The
  Pennsylvania State University, University Park, PA 16802, USA}
\altaffiltext{3}{Penn State Astrobiology Research Center, The
  Pennsylvania State University, University Park, PA 16802, USA}

@@

The Exoplanet Orbit Database (EOD) compiles orbital, transit, host star, and other
parameters of robustly dected exoplanets reported in the peer-reviewed
literature. The EOD can be navigated through the Exoplanet Data
Explorer (EDE) Plotter and Table, available on the world wide web at exoplanets.org. The EOD contains data for 1490 confirmed exoplanets as of March 2014.  
The EOD drives from the Catalog of Nearby Exoplanets \citep{Butler2006}, and the first complete documentation for the EOD and the EDE was presented in 
\cite{Wright2011}. Since then, we have expanded the scope of the
EOD to include secondary eclipse parameters, asymmetric uncertainties and etc. The EOD also incorporats the sample of over 3000 \kepler\ Objects of
Interest (KOIs) and other real planets without good orbital parameters such as those detected by microlensing and imaging. Users can download the latest version of the in tire EOD as a
single comma separated value file from the front page of exoplanets.org.

@@

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of March 2014. \kepler\ contributed to a vast
majority of these new discoveries ($> 800$) while providing an
additional sample of over 3000 exoplanet candidates (\kepler\ Objects
of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has thus surpassed the radial velocity (RV) method to become the most fruitful
means of detecting exoplanets. Meanwhile, great promise lies within
the new and future exoplanet surveys and instruments with direct
imaging (e.g., the Gemini Planet Imager, GPI,
\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
fronts of RV and transit exoplanet searches keep expanding (e.g., the
MINiature Exoplanet RV Array, MINERVA, \citealt{Wright2014}; Habitable-zone Planet Finder, HPF, \cite{Mahadevan2012} and the
Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2010}).

% The business of tracking planet discoveries and EOD
This paper describes our continuing efforts since \cite{Butler2006}
and \cite{Wright2011} to maintain the Exoplanet Orbit Database\footnote{See http://expoplanets.org}(EOD)
and the Exoplanets Data Explorer (EDE), to keep track of the exoplanet
discoveries, and to catalog their orbital parameters and host star
properties. There are also other entities devoted to similar efforts,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011} and the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}. As described in \cite{Wright2011}, the EOD is
dedicated to cataloging properties of all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature.

% data access and popularity
The EOD is hosted at exoplanets.org, which also hosts the EDE, an
interactive table with plotting tools for all the EOD exoplanets
as well as confirmed exoplanets, without good orbital parameters and KOIs. The plottable
dataset of exoplanets.org is available for download as a single comma separated value file from the Website front page.\footnote{At
  \url{htt://exoplanets.org/csv-files/exoplanets.csv}.} The EOD is widely
used in exoplanet research (e.g., \citealt{Dawson2013},
\citealt{Howard2013}, \citealt{Kipping2013}, \citealt{Kane2014},
\citealt{Weiss2014}), and the website exoplanets.org is among the most
visited exoplanet databases, with over $47,000$ visits in 2013\footnote{Measured as "visits" by Google Analytics}.

% updates on EOD and the website
Since the documentation described in \cite{Wright2011}, the EOD has expanded its scope: we now do
not require the host star of an exoplanet to be a normal star (e.g.,
exoplanets around pulsars are now included). It now ingestes more
parameters describing the exoplanet systems and their host stars, and some
parameters have been revised or deleted. We describe our updates to the
EOD in Section~\ref{sec:update}. The EDE at exoplanets.org has also
expanded its scope and now includes the \kepler\ exoplanet candidates
(KOIs). We describe these changes in Section~\ref{sec:kepler}. The
website exoplanets.org has gone through major back-end changes since
\cite{Wright2011}, which are described in Section~\ref{sec:website}. We
summarize the updates and possible future improvements in
Section~\ref{sec:summary}.

@@

The scope of the EOD has expanded, and there are three major changes
from what was described in \cite{Wright2011}. Previously, we only
included exoplanets orbiting the ``normal stars", but now we are not
limiting the type of host stars (e.g. we included exoplanets orbiting
neutron stars). Furthermore, in \cite{Wright2011}, we only included
exoplanets that were discovered by the RV and transit methods in the
EOD, but now we also included planets discovered via timing including pulsar planets and those discovered by eclipse timing. In the
future, exoplanets discovered by any other methods with robust
detections and good orbital parameters will also be included in the
EOD including astrometric planets such as beta Pic b. Previously, we required the planets have minimum mass (m$\sin{i}$) smaller than 24\mjup, but now we require the measured mass ratio to be smaller than 24
\mjup$/\msun$ ($< 0.023)$.

The rest of the selection criteria for the EOD remain unchanged. We
still require the planets to have robust detections and well-determined
orbits (though these are not strictly quantitative and sometimes subjective; see Section~2 of
\citealt{Wright2011}). If new evidence comes to light and we are no
longer confident about the planet, we may remove it from EOD, even if the new evidence is not peer reviewed.

The purpose of the EOD has not changed: we aim to provide the readers
with a comprehensive, reliable, and up-to-date database of exoplanets
with good orbital parameters and host star properties. We do not
report \textit{all} the announced exoplanets as we are not trying to
provide ``an encyclopedic presentation of every claimed detection of an
exoplanet" \citep{Wright2011}.

In the following subsections, we describe the newly added and revised
fields since \cite{Wright2011}, and list all fields in
Table~\ref{tab:par}. We divide the fields into categories consistent with the individual planet page on
exoplanets.org. (Figure~\ref{fig:individual} is an example of
individual planet page, which is presented to website users who click on a planet's name). Some fields are not explicitly tabulated on
the page (e.g., the URLs for ADS pages for papers providing the underlying data), but are explicitly listed in the
downloadable {\tt .csv} file (see Section~\ref{sec:intro}). Though we
focus on the EOD in this section, the fields apply to all planets on
exoplanets.org. We follow the definition of orbital elements in
\cite{Wright2013} unless indicated otherwise.

@@

We report general information of when, by whom and how the planets
were discovered and first reported and provide the references for underlying data. We describe the added or
revised fields since \cite{Wright2011} below.

{\bf DISCMETH} field previously reported the method of discovery,
which was either radial velocity or transit. We have replaced DISCMETH
with {\bf PLANETDISCMETH} and \mbox{{\bf STARDISCMETH}} to better
report how exoplanet systems and individual exoplanets are first
discovered. PLANETDISCMETH reports the discovery method for the
planet, wihle STARDISCMETH reports the discovery method for the first
discovered planet around the host star. These fields are stored
in string format and have one of the following values: "RV",
"Transit", "Imaging", "Microlensing", "Timing", or "Astrometry" (no planets have "astrometry" yet).

The {\bf MONTH} field reports the integer month of the
peer-reviewed paper publication date.

{\bf KEPID} stands for KEPler ID, which is the integer number assigned
for a Kepler host star. KEPID is only available for unconfirmed
KOI's imported directly from the Exoplanet Archive by the exoplanet.org backend. Therefore,
none of the EOD planets including confirmed Kepler planets has a KEPID, yet.

{\bf KOI} stands for Kepler Objects of Interest, which is an object
with transit signals detected by \kepler\ but have not been validated to be due to exoplanets. The KOI field defined by the \kepler\ team and showed on the Exoplanet Archive, contains a floating point
number that consists of a whole number designated to the host star
followed by a decimal number denoting a candidate planet. For example,
KOI 102 is a star suspected to host two exoplanets, and KOI 102.01 is
the inner planet candidate and KOI 102.02 is the outer one. Once a
candidate is confirmed, the NAME field of the planet is replaced by
the official \kepler\ ID (``Kepler" followed by a hyphen, an integer
and an lower case letter). The KOI number is then used as
OTHERNAME. For more information, see
Section~\ref{sec:kepler}.

{\bf EOD} is a boolean which indicates whether an exoplanet is included
in the EOD for having well-characterized orbital
parameters, such as the orbital period (PER). We added this field because exoplanets.org
now also includes robustly discovered planets that do not have
well-characterized orbits, and also \kepler\ planet candidates (see
Section~\ref{sec:kepler} for more details).

{\bf MICROLENSING, IMAGING, TIMING and ASTROMETRY} are flags which
indicate that a planet detected via theses method. For example,
MICROLENSING $=$ 1 means the planet is detected in a microlensing
event. Note that planets may be detected with multiple methods.

%------------------------------------------------------------------------------
\subsection{Orbital Parameters (e.g. RV and Transit)}\label{sec:orbit}

We report the orbital parameters that determine the shape of the
planet's orbit. Depending on the detection methods, different sets of
parameters are given by the literature. For instance, if a planet is
detected by the radial velocity method, the semiamplitude, $K$, is
reported, whereas the inclination of the orbit, $i$, is usually only known via the
transit method (although planet-planet interactions and astrometry can also determine it). We describe the added fields since \cite{Wright2011}
below.

{\bf MASS} is the mass of the planet in the unit of Jupiter
mass. Previously, we only reported the minimum mass, ($m\sin{i}$,
MSINI) of the planets. We now report the mass as well when it is
available. For example, if a planet is discovered by microlensing, we
report the actual mass of the planet according to the literature. If a
planet has both radial velocity and transit measurements, we calculate
the mass from the minimum mass $m\sin{i}$ and the orbital inclination
$i$. For convenience of plotting RV and other planets on a common mass scale (see Section~\ref{sec:kepler}, MASS is set to MSINI if the orbital inclination is not known and
the reference for MASS, MASSREF is set to ``Set to MSINI; I unknown''.

Also for plotting convenience, for KOIs without $m\sin{i}$ measured, we estimate their mass using the
mass-radius relation from the literature. For KOIs with $R<4\rearth$, we follow $M_{p}/\mearth=2.69(R_{p}/\rearth)$
from \cite{Weiss2014}; for $4\rearth<R<6\rearth$, we follow $M_{p}/\mearth=(R_{p}/\rearth)^2.06$ from
\cite{Lissauer2011}; and for $6\rearth<R<11.7\rearth$ we follow $M_{p}/\mearth=1756.7*10^{(-1.646*(11.684/(R_{p}/\rearth)-1)^{(1/2.489)})}$
from \cite{Mordasini2012}.

{\bf SEP} is a separation between the host star
and the planet in units of AU. For directly imaged planets, the
literature usually reports the projected separation and we report the
value accordingly.  If SEP is not directly measured but the semi-major
axis ($a$, A) is available, then we set SEP to A with its reference,
SEPREF, set to ``Set to A''.

{\bf I} is the orbital inclination. Previously, only transiting
systems have I measured, but now some non-transiting systems
have I's reported too. For example, one microlensing system,
OGLE-2006-BLG-109L, has I measured \citep{Bennett2010}. Also, one imaging system, $\beta$ Pic, has I measured \citep{Lagrange2009}

{\bf BIGOM} is the longitude of the ascending node ($\Omega$) in units of degrees. At the moment, no planets have this quantity measured, but astrometric orbits (e.g. from GPI) will .

{\bf LAMBDA} is the projected spin-orbit misalignment ($\lambda$) in
the plane of the sky in units of degrees. At the moment, $\lambda$
values are only available for the transiting systems, which are
measured by either the Rossiter-McLaughlin effect
\citep[e.g.,][]{Winn2005} or planet transiting star spots
\citep[e.g.,][]{Sanchis-Ojeda2012}. $\lambda$ is used because
the true spin-orbit angle, defined as the angle between the
stellar spin axis and the orbital axis, is normally not directly
measurable. We follow \cite{Fabrycky2009} where the coordinates are defined as follows: the
$z$-axis points toward the observer, the $x$-axis points along the
intersection of the sky plane and the planet's orbital plane with the
ascending node of the planet having $x<0$, and the $y$-axis completes
a right handed-triad. $\lambda$ is measured clockwise on the sky from
the $y$-axis to the projected stellar rotational axis. $\lambda$ is
not a newly added field to the EOD but we describe it here because we did not
previously report it consistently, since some literature report the ``projected
spin-orbit misalignment" as $\beta = -\lambda$ instead\footnote{e.g. \cite{Moutou2011}, }. We have sorted
these cases out and made sure that our $\lambda$'s are following the
definition of \cite{Fabrycky2009}.

@@

We report the transit parameters, which are available only when the
planet has TRANSIT Boolean equal to true. We describe two added fields since
\cite{Wright2011} below, which are used for KOI's incorporated from the Exoplanet Archive.

@@

{\bf RR} is the ratio of the planetary radius and the stellar
radius. If the transit depth (DEPTH) is not given, we calculate DEPTH
by taking square of RR, but we do not calculate RR from DEPTH.

@@

We have added an entirely new set of fields for secondary
eclipse depths. Previously, due to the limits of instrumentation and limited
sample of exoplanets, there was not much secondary eclipse depth data
available. Since \cite{Wright2011}, as many different surveys have
been launched, more and more secondary eclipse depths at multiple
bands have become available for more and more planets. Therefore, we added
this entire new set of fields. ZZZ Refer to Ming's SE plot.

The {\bf SE} Boolean indicates whether the system has detected secondary
eclipse in any of the two Micron All-Sky Survey (2MASS;
\citealt{Skrutskie2006}) $J$, $H$, and $K_s$, Kepler photometry band,
and 4 Spitzer IRAC bands. Truth indicates the
system has at least one secondary eclipse measurement in the EOD.

{\bf SEDEPTHX} whereas X stands for one of ``J", ``H", ``KS", ``KP", ``36", ``45", ``58", ``80":
these fields are the secondary eclipse depth measured in the
corresponding wavelength band. SEDEPTHJ, H, and KS are the depths
measured in the 2MASS wavelength bands in the near infrared, centered
at 1.25~\micron, 1.65~\micron, and 2.15~\micron, respectively. KP is
the depth measured in the \kepler\ photometric band which spans 400 to 865~nm. The other four represent the Spitzer IRAC and MIPS bands centered at
3.6~\micron, 4.5~\micron, 5.8~\micron, and 8.0~\micron.

{\bf SET} is the epoch of secondary eclipse center, normally given in HJD but (as with other fields) when the literature reports HJD or UTC JD, we do not attempt a conversion to BJD.

@@

This set of parameters provides users the physical parameters of
the exoplanet host stars.  Most of the parameters are derived from the
stellar models in the literature and we provide the readers with the
references. We describe added fields since \cite{Wright2011} below.

{\bf GAMMA} ($\gamma$) is the radial velocity of the center of mass of
the planetary system with respect to the barycentric frame and is reported in km/s.

{\bf RSTAR} is the radius of the star in the solar units.

{\bf RHOSTAR} is the density of the star in g/cm$^3$.

@@

We provide the brightness of the host star measured in different
filters. We report optical magnitude and color ($V$ and $B-V$),
2MASS $J$, $H$, and $K_s$ magnitudes and, we have added {\bf KP}. Notes that the definitions of V and B in the literature vary, and are often Hipparcos values
(the stellar magnitude measured through the \kepler\ bandpass).

@@

We report the coordinates of the host star as well as the host star's
ID as designated by different catalogs.  We added the {\bf DIST} field since
\cite{Wright2011}, which is the distance to the host star in the unit
of pc. If only parallax (PAR) is given, we calculate DIST based on PAR
and vice versa. If the literature does not report DIST or PAR, then we
obtain PAR from the Hipparcos dataset by \cite{van Leeuwen2009} for stars with Hipparcos numbers. We
naively propagate the error in PAR to DIST and vice versa.

@@

We have changed the way of reporting uncertainties, especially
asymmetric ones since \cite{Wright2011}. We now report
uncertainties for a certain field X as XUPPER, XLOWER and UX. XUPPER
and XLOWER store the upper and lower 1$\sigma$ uncertainties, and they
are different when the error bars are asymmetric. UX contains the
1$\sigma$ uncertainty, and it equals $({\rm XUPPER+XLOWER})/2$ in
the case of asymmetric error bars. Fields that have XUPPER, XLOWER and
UX are: all the orbital parameters, all the transit parameters, all the
secondary eclipse fields, and all the stellar
properties and DIST and PAR.

We also report the upper limits (XUL) for planet minimum mass (MSINI),
eccentricity (ECC), and the radial velocity semi-amplitude (K) when
the literature reports them. For example, the upper limits for ECC is
reported when the orbit is consistent with a circular one, and the
upper limits for K is reported when there is only upper-limit radial
velocity detection. If only upper limits are given, we set the
parameter field X to 0, the uncertainty XU to half of the upper limit,
and the upper error bar XUPPER to the upper limits (same as XUL). For
example, if the literature reports the upper limit for ECC, which we
report in ECCUL, then we set ECC to be 0, ECCUPPER to ECCUL, and UECC
to ECCUL/2. Since not all authors define the upper limits in the same
way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
readers to refer to the original references for more information. Note that as of this writing, limits have not been incorporated into the EDE (see Section~\ref{sec:}
